Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-03 docs/evol.tex
Add architecture figure to text
minor changes

%\begin{figure}
%	\includegraphics{arch.pdf}
%\end{figure}

@@

First, we scanned the Maven repository for appropriate {\sc jar}s and created a
list that included them. We discuss the {\sc jar} selection process in the next 
section. With the {\sc jar} list at hand, we created a series of processing tasks
and added them to the task queue. Then we executed twenty five (Unix-based)
workers that checked out tasks from the queue, processed the data and stored the
results to the data repository.

A typical processing cycle of a worker included the following steps: after
the worker spawned, it requested a task from the queue. This task contained
the {\sc jar} name, which was typically a project version that was downloaded locally.
First, specific {\sc jar} metadata were calculated and stored. Such metadata included
its size, its dependencies, and a number that represented the chronological order of the
release. This order was derived from an {\sc xml} file that
accompanies every project in the Maven repository called {\it
maven-metadata.xml}. Then, FindBugs was invoked by the worker and its results were
also stored in the data repository. When the task was completed the queue
was notified and the next task was requested.

>>>>

@@

First, we scanned the Maven repository for appropriate {\sc jar}s and created a
list that included them. We discuss the {\sc jar} selection process in the next 
section. With the {\sc jar} list at hand, we created a series of processing tasks
and added them to the task queue. Then we executed twenty five (Unix-based)
workers that checked out tasks from the queue, processed the data and stored the
results to the data repository (see Figure~\ref{fig:arch}).

\begin{figure}[t]
  \begin{center}
    \includegraphics[scale=0.7]{figures/arch.pdf}
  \end{center}
  \caption{The Data Processing Architecture}
  \label{fig:arch}
\end{figure}

A typical processing cycle of a worker included the following steps: after
the worker spawned, it requested a task from the queue. This task contained
the {\sc jar} name, which was typically a project version that was downloaded locally.
First, specific {\sc jar} metadata were calculated and stored. Such metadata included
its size, its dependencies, and a number that represented the chronological order of the
release. This order was derived from an {\sc xml} file that
accompanies every project in the Maven repository called {\it
maven-metadata.xml}. Then, FindBugs was invoked by the worker and its results were
also stored in the data repository. When the task was completed the queue
was notified and the next task was requested. A schematic representation
of the data processing architecture can be seen in Figure~\ref{fig:arch}.
